Meta-analysis

### 2019-07-22 05_MetaAnalysis.Rmd
Addition of standard deviation to sample Variance chunk

```{r Meta_dataImport}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

str(PM_MB_means)
```

@@

@@

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)

@@

@@

>>>>

```{r Meta_dataImport}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)

#str(PM_MB_means)
```

@@

The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment. The following code attempts to convert this to sampling variance as per the method in

@@

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)
MSE <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

@@

# and replacing the values in the dataset

PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Y_error.type <- "SamplingVariance"

@@

Now to estimate the variance from the standard deviation

```{r stdev2SampVariance}
# subset data by those which describe the Yield error with standard deviation
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          Y_error.type == "stdev")%>%
   select(Trial_ref)%>%
   distinct()

# calculate the Sampling variance from the standard deviation
# standard error of the mean equals the standard deviation divided by the square root of the number of samples
# Sv <- sem^2 <- stdev/sqrt(n)
# Sampling variance eqauls the square of the standard error.
# Sv <- (stdev/sqrt(n))^2

# Therefore

for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error)){
# create empty vector at first iteration with length of j
   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error))}

# Equation to convert standard deviation to Sampling Variance 
   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error/
               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates))^2
   }

PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <-

   # and replacing the values in the dataset
PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Y_error.type <- "SamplingVariance"
